---
title: 'Problem Set #4 - Yannie Lee'
author: 'Experiment Design: Alex & Coco'
output:
  pdf_document: 
    latex_engine: xelatex
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(tidy.opts=list(width.cutoff=60),tidy=TRUE,echo = TRUE)
```

```{r}
# load packages 
library(foreign)
```
```{r, message=FALSE}
library(stargazer)
#Define Useful Funcions
RobustSE <- function(model){
  #plot(model, which =2) #errors are no homoskedastic, so compute robust standard errors
  model$se = sqrt(diag((vcov(model))))
  stargazer(model, se=list(model$se), header=F, type="text")
}
```

```{r}
data <- read.csv("./Final_Project_data_v2.csv")
head(data)
data
``` 
b0 = baseline blood pressure (before treatments)
b1 = change in blood pressure due to watching mindfulness video before social media consumption
b2 = change in blood pressure due to 5 minutes of social media consumption
b3 = change in blood pressure due to watching mindfulness video after social media consumption

The assumptions needed to identify this causal effect based on the within-subject design are:
- no anticipation - which means that the potential outcome are unaffected by treatments that are administered in the future
(when social media is first, no impact on facebook changes in future + vice versa)
- no persistence - potential outcomes in one period are unaffected by previous treatments

```{r}
#eda
table <- xtabs(~data$Race + data$Gender)
table
23+13+12

table <- xtabs(~ data$Age)
table
hist(data$Age, breaks  = 20, main = "Histogram of Age Data", xlab = "Age")

table <- xtabs(~ data$facebook.usage)
table
table <- xtabs(~ data$meditation)
table

table <- xtabs(~ data$facebook.usage + data$meditation)
table

table <- xtabs(~ data$marital_status + data$no.of.kids)
table

sum(data$Meditation_first)
sum(data$Facebook_First)
```

```{r}
fit_b1 <- lm(BP2 ~ b1+b2_social_media+b3, data=data)
summary(fit_b1)

fit_b2 <- lm(BP2 ~ BP0 + Meditation_first, data=na.omit(data))
summary(fit_b2)

###
#covariate adjusted models
#male/female
#asian, caucasion
#meditation familiarity

fit_b2 <- lm(I(BP1 - BP0) ~  Meditation_first, data=na.omit(data))
RobustSE(fit_b2)

fit_b2 <- lm(b3_meditation ~  Meditation_first, data=na.omit(data))
RobustSE(fit_b2)

fit_b2 <- lm(b2_social_media ~  Meditation_first, data=na.omit(data))
RobustSE(fit_b2)


``` 



```{r}
library(data.table)
data <- read.csv("./Final_Project_data_v2.csv")
fpdt<-as.data.table(data)
fpdt[,BPbase:=BP0]
fpdt[Meditation_First=='Y',`:=`(BPmind=BP1, BPsocial=BP2, BPmind1=BP1)]
fpdt[Meditation_First=='N',`:=`(BPmind=BP2, BPsocial=BP1, BPmind2=BP2)]
# interaction model
melted<-melt(fpdt, measure.vars=c('BPbase', 'BPmind', 'BPsocial'), id.vars=c('subject', 'Gender', 'Meditation_first'))
model_interaction<-lm(value ~ Meditation_first*variable + subject, data=melted)
# David's model
melted<-melt(fpdt, measure.vars=c('BPbase', 'BPmind1', 'BPsocial', 'BPmind2'))
model_original<-lm(value ~ variable + Gender + marital_status, data=na.omit(melted))
summary(model_original)

table(data$marital_status)

rawdt[,.(base_mean=mean(BP0), base_stdev=sd(BP0), base_median=median(BP0)),by=Meditation_First]

na.omit(rawdt[,.(Meditation_First, map0=(map0a+map0b)/2)])[,.(base_mean=mean(map0), base_stdev=sd(map0), base_median=median(map0)),by=Meditation_First]
```

